Technologies of Semantic WEB as an environment of application development and integration

### 2021-11-23 paper-aicts-cherkashin.tex
Added architecture figure.

Some general words about architectures .... related to WEB.

@@

\subsection{Knowledge graph properties as application basis}
\label{sec:kg-as-basis}

@@

>>>>

Some general words about architectures .... related to WEB.  Modeled with component architecture.

@@

% \subsection{Knowledge graph properties as application basis}
% \label{sec:kg-as-basis}

@@

\begin{figure}[bth]
  \begin{center}
    \includegraphics[width=0.9\linewidth]{architecture-mda-lod-ext-general.pdf}
  \end{center}
  \begin{center}
      \textbf{Abbreviations}\\[1ex]\scriptsize
      T-Module is Transformation module,
      MDA is Model-Driven Architecture,
      CIM is Computationally Independent Model,
      PIM is Platform Independent Model,
      PSM is Platform Specific Model,
      T-Box is Terminological Box,
      A-Box is Instance Box,
      A-Box is Instance Box,
      NGS is Next-Generation Sequencing,
      DB is Database.
  \end{center}

  \caption{Architecture of services}
  \label{fig:arch-services}
\end{figure}
